---
title: "EX 3"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
editor: visual
toc: true
toc-depth: 2
toc-title: Contents
---

```{r, warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, here, effectsize, psych, gmodels, doSPSS)
Data <- read_csv(here('Data\\dataForAnalysis.csv'))

```

# METI

## Reliability

```{r, warning=FALSE, message=FALSE}
METI <- 
Data %>% 
  select(METI_1_1, METI_1_2, METI_1_3, METI_1_4, METI_1_5, METI_1_6, METI_1_7, METI_1_8, METI_2_1, METI_2_2, METI_2_3, METI_2_4, METI_2_5, METI_2_6, METI_2_7, METI_2_8) %>% 
  alpha()

METI$total
```

## METI Total: Descriptive statistics + t.test + effect size + histogram

### Questions direction is positive to Dont know advisor

```{r, warning=FALSE, message=FALSE}


descriptiveStats <- 
Data %>% 
  summarise(Mean = round(mean(METI), 2),
            SD = round(sd(METI), 2),
            Med = round(median(METI), 2),
            N =  nrow(Data))

descriptiveStats

Model <- 
Data %>% 
  pull(METI) %>% 
  t.test(mu = 4)

Model

effectsize(Model)

Data %>% 
  ggplot(aes(x = METI)) + 
  geom_histogram() + 
  geom_vline(xintercept = descriptiveStats$Mean, linetype="dotted", 
                color = "red", size=1.5) + 
  geom_vline(xintercept = descriptiveStats$Med, linetype="dashed", 
                color = "red", size=1.5) +
  geom_vline(xintercept = c(descriptiveStats$Mean + descriptiveStats$SD), linetype="dotted", 
                color = "blue", size=1.5) + 
  geom_vline(xintercept = c(descriptiveStats$Mean - descriptiveStats$SD), linetype="dotted", 
                color = "blue", size=1.5) + 
  theme_bw()
```

## First choice \* METI

```{r, warning=FALSE, message=FALSE}
indttest(Data$METI, Data$DV_1, Parametric = FALSE)
```

## Second choice \* METI

```{r, warning=FALSE, message=FALSE}
indttest(Data$METI, Data$DV_2, Parametric = FALSE)
```

## Change choice \* METI

```{r, warning=FALSE, message=FALSE}
oneWayAnova(Data$METI, Data$changeDV, Parametric = FALSE)
```

## METI per question

### Questions direction is positive to Dont know advisor

### All significant with p adjusted for bonfferoni

```{r, warning=FALSE, message=FALSE}
bonfferoniCorrection <- 0.05 / 16
minimalCohensD <- 0.3
for (i in c('METI_1_1', 'METI_1_2', 'METI_1_3', 'METI_1_4', 'METI_1_5', 'METI_1_6', 'METI_1_7', 'METI_1_8', 'METI_2_1', 'METI_2_2', 'METI_2_3', 'METI_2_4', 'METI_2_5', 'METI_2_6', 'METI_2_7', 'METI_2_8')) {
  Y <- Data[, i] %>% unlist()
  test <- wilcox.test(x = Y, mu = 4)
  # d    <- effectsize(test)
  if(test$p.value < bonfferoniCorrection ){  # d$d >= minimalCohensD

    Mean <- round(mean(Data[, i] %>% unlist()), 1)
    SD   <- round(sd(Data[, i] %>% unlist()), 1)

    Data[, i] %>% unlist() %>% hist(main = paste0(i, '; Mean=', Mean, ', SD=', SD))
    
    # Data[, i] %>% unlist() %>% hist(main = paste0(i, '; Mean=', Mean, ', SD=', SD, ', d=', round(d$d, 2)))
  }
}

```

# Intellectual Humility

## Reliability

```{r, warning=FALSE, message=FALSE}
IH <- 
Data %>% 
  select(IH_1, IH_2, IH_3, IH_4, IH_5, IH_6) %>% 
  alpha()
IH$total
```

## Intellectual Humility \~ Advisor preference: Descriptive statistics + Mann Whintey test

### First choice \* Intellectual Humility

```{r, warning=FALSE, message=FALSE}
indttest(Data$IH, Data$DV_1, Parametric = FALSE)
```

### Second choice \* Intellectual Humility

```{r, warning=FALSE, message=FALSE}
indttest(Data$IH, Data$DV_2, Parametric = FALSE)
```

### Change choice \* Intellectual Humility

```{r, warning=FALSE, message=FALSE}
oneWayAnova(Data$IH, Data$changeDV, Parametric = FALSE)
```

# Chi square for goodness of fit: DV = Advisor preferation

## Table, Model, Effect size

### First choice

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_1, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_1), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

### Second choice

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_2, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_2), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')

```

### First choice \* Second choice

```{r}
CT(rowFactor = Data$DV_1, colFactor = Data$DV_2)
```

# Change preferation

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$changeDV, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$changeDV), p = c(1 / 3, 1 / 3, 1 / 3), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

# Chi square for goodness of fit: DV = Who made more errors

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$whoErrors, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$whoErrors), p = c(0.25, 0.25, 0.25, 0.25), correct = FALSE)
Model
effectsize(Model, 'normalized_chi', test = 'all')
```

# Chi square for goodness of fit: DV = Advisor preferation: for Pp who said that the advisor who made more errors is the advisor who know

## First choice

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_1[Data$whoErrors == 'knowError'], format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_1[Data$whoErrors == 'knowError']), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

## Second choice

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_2[Data$whoErrors == 'knowError'], format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_2[Data$whoErrors == 'knowError']), p = c(0.5, 0.5), correct = FALSE)
Model
```

## Change preferation

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$changeDV[Data$whoErrors == 'knowError'], format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$changeDV[Data$whoErrors == 'knowError']), p = c(1 / 3, 1 / 3, 1 / 3), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

# Chi square for goodness of fit: DV = Advisor preferation: for Pp who said that the two advisors made the same number of mistakes

```{r, warning=FALSE, message=FALSE}
# CrossTable(Data$DV_1[Data$whoErrors != 'knowError'], format = 'SPSS', chisq = TRUE)
# Model <- chisq.test(table(Data$DV_1[Data$whoErrors != 'knowError']), p = c(0.5, 0.5), correct = FALSE)
# Model
# effectsize(Model, 'normalized_chi')
```

```{r, warning=FALSE, message=FALSE}
# CrossTable(Data$DV_2[Data$whoErrors != 'knowError'], format = 'SPSS', chisq = TRUE)
# Model <- chisq.test(table(Data$DV_2[Data$whoErrors != 'knowError']), p = c(0.5, 0.5), correct = FALSE)
# Model
# effectsize(Model, 'normalized_chi')
```

# Chi square for independence: Advisor preferation \* Advisor errors

```{r, warning=FALSE, message=FALSE}
# CT(Data$whoErrors, Data$DV_1)
```

```{r, warning=FALSE, message=FALSE}
# CT(Data$whoErrors, Data$DV_2)
```

```{r, warning=FALSE, message=FALSE}
# CT(Data$whoErrors, Data$changeDV)
```

# Chi square for goodness of fit: DV = face decision task

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$faceDecision, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$faceDecision), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

# Chi square for independence: Advisor preferation \* face decision task

## First choice

```{r, warning=FALSE, message=FALSE}
CT(Data$faceDecision, Data$DV_1)
```

## Second choice

```{r, warning=FALSE, message=FALSE}
CT(Data$faceDecision, Data$DV_2)
```

## Change preferation

```{r, warning=FALSE, message=FALSE}
CT(Data$changeDV, Data$faceDecision)
```

# Controls

## Age \~ Avisor preferece: Descriptive statistics + Mann Whintey test

### First choice \* Age

```{r, warning=FALSE, message=FALSE}

indttest(Data$Age, Data$DV_1, Parametric = FALSE)

```

### Second choice \* Age

```{r, warning=FALSE, message=FALSE}

indttest(Data$Age, Data$DV_2, Parametric = FALSE)

```

### Change choise \* Age

```{r, warning=FALSE, message=FALSE}

oneWayAnova(Data$Age, Data$changeDV, Parametric = FALSE)

```

## Gender \~ Avisor preferece: Descriptive statistics + Mann Whintey test

### First choice \* Gender

```{r, warning=FALSE, message=FALSE}

CT(Data$DV_1[Data$Gender != 'Other'], Data$Gender[Data$Gender != 'Other'])

```

### Second choice \* Gender

```{r, warning=FALSE, message=FALSE}

CT(Data$DV_2[Data$Gender != 'Other'], Data$Gender[Data$Gender != 'Other'])

```

### Change choice \* Gender

```{r, warning=FALSE, message=FALSE}

CT(Data$changeDV[Data$Gender != 'Other'], Data$Gender[Data$Gender != 'Other'])

```

## Understanding market \~ Avisor preference: Descriptive statistics + Mann Whintey test

### First choice \* Understanding market

```{r, warning=FALSE, message=FALSE}

indttest(Data$marketUnderstanding, Data$DV_1, Parametric = FALSE)

```

### Second choice \* Understanding market

```{r, warning=FALSE, message=FALSE}

indttest(Data$marketUnderstanding, Data$DV_2, Parametric = FALSE)

```

### Change choice \* Understanding market

```{r, warning=FALSE, message=FALSE}

oneWayAnova(Data$marketUnderstanding, Data$changeDV, Parametric = FALSE)

```

# Multivariate models

## First choice: Prefere Know \~ IH + Gender + Age + Market Understanding

```{r, warning=FALSE, message=FALSE}

logReg(Data$DV_1[Data$Gender != 'Other'], Predictors = Data[Data$Gender != 'Other', c('IH', 'Gender', 'Age', 'marketUnderstanding')])

```

## Second choice: Prefere Know \~ IH + Gender + Age + Market Understanding

```{r, warning=FALSE, message=FALSE}

logReg(Data$DV_2[Data$Gender != 'Other'], Predictors = Data[Data$Gender != 'Other', c( 'IH', 'Gender', 'Age', 'marketUnderstanding')])


```
