---
title: "Chi square"
output:
  html_document:
    code_folding: hide
date: '2022-07-16'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, here, effectsize, psych, gmodels, doSPSS)
Data <- read_csv(here('Data\\dataForAnalysis.csv'))
```

# Chi square for goodness of fit: DV = Advisor preferation
## Table, Model, Effect size
### First choise
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_1, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_1), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```
### Second choise
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_2, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_2), p = c(0.5, 0.5), correct = FALSE)
Model
```

### First choise * Second choise
```{r}
CT(rowFactor = Data$DV_1, colFactor = Data$DV_2)
```

# Chnage preferation
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$changeDV, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$changeDV), p = c(0.25, 0.25, 0.25, 0.25), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

# Chi square for goodness of fit: DV = Who made more errors

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$whoErrors, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$whoErrors), p = c(0.25, 0.25, 0.25, 0.25), correct = FALSE)
Model
effectsize(Model, 'normalized_chi', test = 'all')
```

# Chi square for goodness of fit: DV = Advisor preferation: for Pp who said that the advisor who made more errors is the advisor who know
## First choise
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_1[Data$whoErrors == 'knowError'], format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_1[Data$whoErrors == 'knowError']), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

## Second choise
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$DV_2[Data$whoErrors == 'knowError'], format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$DV_2[Data$whoErrors == 'knowError']), p = c(0.5, 0.5), correct = FALSE)
Model
```

## Change preferation
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$changeDV[Data$whoErrors == 'knowError'], format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$changeDV[Data$whoErrors == 'knowError']), p = c(0.25, 0.25, 0.25, 0.25), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

# Chi square for goodness of fit: DV = Advisor preferation: for Pp who said that the two advisors made the same number of mistakes
```{r, warning=FALSE, message=FALSE}
# CrossTable(Data$DV_1[Data$whoErrors != 'knowError'], format = 'SPSS', chisq = TRUE)
# Model <- chisq.test(table(Data$DV_1[Data$whoErrors != 'knowError']), p = c(0.5, 0.5), correct = FALSE)
# Model
# effectsize(Model, 'normalized_chi')
```

```{r, warning=FALSE, message=FALSE}
# CrossTable(Data$DV_2[Data$whoErrors != 'knowError'], format = 'SPSS', chisq = TRUE)
# Model <- chisq.test(table(Data$DV_2[Data$whoErrors != 'knowError']), p = c(0.5, 0.5), correct = FALSE)
# Model
# effectsize(Model, 'normalized_chi')
```


# Chi square for independece: Advisor preferation * Advisor errors

```{r, warning=FALSE, message=FALSE}
# CT(Data$whoErrors, Data$DV_1)
```

```{r, warning=FALSE, message=FALSE}
# CT(Data$whoErrors, Data$DV_2)
```

```{r, warning=FALSE, message=FALSE}
# CT(Data$whoErrors, Data$changeDV)
```

# Chi square for goodness of fit: DV = face decision task

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$faceDecision, format = 'SPSS', chisq = TRUE)
Model <- chisq.test(table(Data$faceDecision), p = c(0.5, 0.5), correct = FALSE)
Model
effectsize(Model, 'normalized_chi')
```

# Chi square for independece: Advisor preferation * face decision task
## First choise
```{r, warning=FALSE, message=FALSE}
CT(Data$faceDecision, Data$DV_1)
```

## Second choise
```{r, warning=FALSE, message=FALSE}
CT(Data$faceDecision, Data$DV_2)
```

## Change preferation
```{r, warning=FALSE, message=FALSE}
CT(Data$changeDV, Data$faceDecision)
```
