---
title: "Untitled"
author: "Tom Mushkat"
date: '2022-07-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, here, doSPSS)
Data <- read_csv(here('Data\\dataForAnalysis.csv'))
```

## Age ~ Avisor preferece: Descriptive statistics + Mann Whintey test
### First choise * Age
```{r, warning=FALSE, message=FALSE}

indttest(Data$Age, Data$DV_1, Parametric = FALSE)

```

### Second choise * Age
```{r, warning=FALSE, message=FALSE}

indttest(Data$Age, Data$DV_2, Parametric = TRUE)

```

### Change choise * Age
```{r, warning=FALSE, message=FALSE}

oneWayAnova(Data$Age, Data$changeDV, Parametric = FALSE)

```

## Gender ~ Avisor preferece: Descriptive statistics + Mann Whintey test
### First choise * Gender
```{r, warning=FALSE, message=FALSE}

CT(Data$DV_1[Data$Gender != 'Other'], Data$Gender[Data$Gender != 'Other'])

```

### Second choise * Gender
```{r, warning=FALSE, message=FALSE}

CT(Data$DV_2[Data$Gender != 'Other'], Data$Gender[Data$Gender != 'Other'])

```

### Change choise * Gender
```{r, warning=FALSE, message=FALSE}

CT(Data$changeDV[Data$Gender != 'Other'], Data$Gender[Data$Gender != 'Other'])

```


## Understanding market ~ Avisor preferece: Descriptive statistics + Mann Whintey test
### First choise * Gender
```{r, warning=FALSE, message=FALSE}

indttest(Data$marketUnderstanding, Data$DV_1, Parametric = FALSE)

```

### Second choise * Gender
```{r, warning=FALSE, message=FALSE}

indttest(Data$marketUnderstanding, Data$DV_2, Parametric = FALSE)

```

### Change choise * Gender
```{r, warning=FALSE, message=FALSE}

oneWayAnova(Data$marketUnderstanding, Data$changeDV, Parametric = FALSE)

```


# Logistic regression
## First choise: Prefere Know ~ METI + IH + Gender + Age + Market Understanding
```{r, warning=FALSE, message=FALSE}

logReg(Data$DV_1[Data$Gender != 'Other'], Predictors = Data[Data$Gender != 'Other', c('METI', 'IH', 'Gender', 'Age', 'marketUnderstanding')])

```

## Second choise: Prefere Know ~ METI + IH + Gender + Age + Market Understanding
```{r, warning=FALSE, message=FALSE}

logReg(Data$DV_2[Data$Gender != 'Other'], Predictors = Data[Data$Gender != 'Other', c('METI', 'IH', 'Gender', 'Age', 'marketUnderstanding')])


```
