---
title: "Questionaires"
output:
  html_document:
    code_folding: hide
date: '2022-07-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, here, effectsize, psych, gmodels, doSPSS)
Data <- read_csv(here('Data\\dataForAnalysis.csv'))

```

# METI
## Reliability
```{r, warning=FALSE, message=FALSE}
Data %>% 
  select(METI_1_1, METI_1_2, METI_1_3, METI_1_4, METI_1_5, METI_1_6, METI_1_7, METI_1_8, METI_2_1, METI_2_2, METI_2_3, METI_2_4, METI_2_5, METI_2_6, METI_2_7, METI_2_8) %>% 
  alpha()
```

## METI Total: Descriptive statistics + t.test + effect size + histogram
### Questions direction is positive to Dont know advisor
### In Red the mean and median, in blue standard deviation
```{r, warning=FALSE, message=FALSE}


descriptiveStats <- 
Data %>% 
  summarise(Mean = round(mean(METI), 2),
            SD = round(sd(METI), 2),
            Med = round(median(METI), 2),
            N =  nrow(Data))

descriptiveStats

Model <- 
Data %>% 
  pull(METI) %>% 
  t.test(mu = 4)

Model

effectsize(Model)

Data %>% 
  ggplot(aes(x = METI)) + 
  geom_histogram() + 
  geom_vline(xintercept = descriptiveStats$Mean, linetype="dotted", 
                color = "red", size=1.5) + 
  geom_vline(xintercept = descriptiveStats$Med, linetype="dashed", 
                color = "red", size=1.5) +
  geom_vline(xintercept = c(descriptiveStats$Mean + descriptiveStats$SD), linetype="dotted", 
                color = "blue", size=1.5) + 
  geom_vline(xintercept = c(descriptiveStats$Mean - descriptiveStats$SD), linetype="dotted", 
                color = "blue", size=1.5) + 
  theme_bw()
```

## First choise * METI 
```{r, warning=FALSE, message=FALSE}
indttest(Data$METI, Data$DV_1, Parametric = FALSE)
```

## Second choise * METI 
```{r, warning=FALSE, message=FALSE}
indttest(Data$METI, Data$DV_2, Parametric = FALSE)
```

## Change choise * METI 
```{r, warning=FALSE, message=FALSE}
oneWayAnova(Data$METI, Data$changeDV, Parametric = FALSE)
```

## METI per question
### Questions direction is positive to Dont know advisor
### All significant with p adjusted for bonfferoni and d > 0.3
```{r, warning=FALSE, message=FALSE}
bonfferoniCorrection <- 0.05 / 16
minimalCohensD <- 0.3
for (i in c('METI_1_1', 'METI_1_2', 'METI_1_3', 'METI_1_4', 'METI_1_5', 'METI_1_6', 'METI_1_7', 'METI_1_8', 'METI_2_1', 'METI_2_2', 'METI_2_3', 'METI_2_4', 'METI_2_5', 'METI_2_6', 'METI_2_7', 'METI_2_8')) {
  
  test <- t.test(x = Data[, i], mu = 4)
  d    <- effectsize(test)
  if(test$p.value < bonfferoniCorrection & d$d >= minimalCohensD){

    Mean <- round(mean(Data[, i] %>% unlist()), 1)
    SD   <- round(sd(Data[, i] %>% unlist()), 1)

    Data[, i] %>% unlist() %>% hist(main = paste0(i, '; Mean=', Mean, ', SD=', SD, ', d=', round(d$d, 2)))
  }
}

```

# Intellectual Humility
## Reliability
```{r, warning=FALSE, message=FALSE}
Data %>% 
  select(IH_1, IH_2, IH_3, IH_4, IH_5, IH_6) %>% 
  alpha()
```

## Intellectual Humility ~ Avisor preferece: Descriptive statistics + Mann Whintey test
### First choise * Intellectual Humility 
```{r, warning=FALSE, message=FALSE}
indttest(Data$IH, Data$DV_1, Parametric = FALSE)
```

### Second choise * Intellectual Humility 
```{r, warning=FALSE, message=FALSE}
indttest(Data$IH, Data$DV_2, Parametric = FALSE)
```

### Change choise * Intellectual Humility 
```{r, warning=FALSE, message=FALSE}
oneWayAnova(Data$IH, Data$changeDV, Parametric = FALSE)
```
